Multiple Linear Regression on Sleep Data

### 2025-05-08 paper/paper.qmd
adding in table for coefficients of final model

final_model <- lm(sleep_duration ~ ., data = sleep_test_final)
summary(final_model)
```

>>>>

final_model <- lm(sleep_duration ~ ., data = sleep_test_final)

tidy(final_model) %>%
  dplyr::select(term, estimate, p.value) %>%
  kable(
    digits = 3,
    caption = "Coefficients and P-values from Linear Model",
    booktabs = TRUE,
    format = "latex",
    escape = TRUE
  )
